---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# yyyymm

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Codecov test coverage](https://codecov.io/gh/jbkunst/yyyymm/branch/master/graph/badge.svg)](https://codecov.io/gh/jbkunst/yyyymm/branch/master)
[![R build status](https://github.com/jbkunst/yyyymm/workflows/R-CMD-check/badge.svg)](https://github.com/jbkunst/yyyymm/actions?workflow=R-CMD-check)
<!-- badges: end -->

The goal of `yyyymm::` is to make life easier with period format.

## Installation


``` r
source("https://install-github.me/jbkunst/yyyymm")
```

## Examples

This is a basic example which shows you how to solve a common problem:


### `ym_to_date`

```{r}
library(yyyymm)
ym_to_date(ym = c(200902, 201912), day = 1)
```

### `ym_diff`

```{r}
ym_diff(ym = c(200902, 201912), ym2 = c(200901, 201712))
```

### `ym_add_months`

```{r}
ym_add_months(c(200902, 201912), months = c(1, -12))
```

### `ym_format`

```{r}
ym_format(c(200902, 201912), "%B %Y")
```

### `ym_seq`

```{r}
ym_seq(201303, 201512)
```

### `ym_div`

```{r}
seqym <- ym_seq(201303, 201512)
seqym

ym_div(seqym, ng = 3)

ym_div(seqym, ng = 4)
```


### `is_yyyymm`

```{r, error=TRUE}
yyyymm:::is_yyyymm(999)

yyyymm:::is_yyyymm(1111111)

yyyymm:::is_yyyymm(201900)

yyyymm:::is_yyyymm(201913)

yyyymm:::is_yyyymm(201913.5)
```

## Code of Conduct

Please note that `yyyymm::` project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
